Type theory in type theory with single substitutions

### 2024-09-17 types_2024_postproc/p.tex
stuff

\subsection{Models}

TODO: To make sure that our definitions of models are correct, we show
that in Agda there is a model for both the parallel and single
substitution calculi.

@@

  modelled by $\top$, its $\eta$ law holds 

@@

\section{Conclusions}
\label{sec:conclusion}

>>>>

As a sanity check for our notion of SSC-model, we defined the standard
(metacircular \cite{DBLP:conf/popl/AltenkirchK16}) model of the
SSC-based calculus calculus in Agda. We used the techniques of Kovács
\cite{DBLP:conf/csl/Kovacs22} to define inductive-recursive universes
to model the infinite hierarchy of types, and all the SSC-equations
hold by reflexivity in this model. We defined the analogous CwF-based
standard model.

@@

  modelled by $\top$, its $\eta$ law holds via $\eta$ for $\top$.

@@

\section{Conclusions and further work}
\label{sec:conclusion}
